---
title: "Week 2 Project"
author: "David Elliott"
date: "December 21, 2016"
output: html_document
---

# Sasquatch, aka. Bigfoot, aka. Gigantopithecus sightings!!!
Each Class A reported sighting is marked by a foot icon. Click on the icon for a URL to more information!!!

```{r options}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r map}
gps <- read.csv("Bigfoot Reports Class A.csv", header=FALSE)
gps <- gps[,1:3]
colnames(gps)[1] <- 'long'
colnames(gps)[2] <- 'lat'
LatLong <- gps[,1:2]

library(stringr)
url_pattern <- "http://.*"
LatLong$ContentURL <- str_extract(gps[,3], "https?:\\/\\/\\S*")

library(leaflet)

Icon <- makeIcon(
        iconUrl = "foot-print-308596_640.png",
        iconWidth = 18, iconHeight = 20,
        iconAnchorX = 18/2, iconAnchorY = 16 
)

Sites <- as.character(LatLong$ContentURL)


LatLong %>%
        leaflet() %>%
        addTiles() %>%
        addMarkers(icon = Icon, popup = Sites)
```

CREDIT: These data were obtained from the Bigfoot Field Researchers Organization (BFRO). More info http://www.bfro.net/

DISCLAIMER: The author of this analysis makes no claims as to the validity or accuracy of the results. Remember, trash in, trash out.